COG-ED Manuscript

### 2022-02-15 06_Paper/COG-ED/Manuscript.Rmd
Update Manuscript.Rmd

To determine the influence of task performance in the association of SVs and n-back level, we will set up a MLM using the $lmerTest$ package [@Kuznetsova2017]. 
We will apply restricted maximum likelihood (REML) to fit the model.
First, we will calculate the intraclass correlation (ICC) on the basis of the null model. <!--CS: Wieso wird der ICC nur für das Null Modell berechnet ? Man könnte den doch auch für das full-model ebenfalls angeben und sehen, wieviel Varianzaufklärung hinzugekommen ist? -->
Second, we will estimate a random slopes model of SVs including n-back load level as level-1-predictor and, additionally, NFC as level-2-predictor. 
Within the model, we will control for *d'*, RT, correct, and post-correct trials.
$$
SV \sim level\ * NFC + d' + RT + correct + postcorrect + (level|subject)
$$
Level-1-predictors will be centered within cluster, whereas the level-2-predictor will be centered at the grand mean as recommended by Enders & Tofighi [-@Enders2007]. 
We will visually inspect the residuals of the final model.
The approximately normal distribution indicates no evidence to perform model criticism.  
Third, we will perform a simple slopes analysis with n-back level as predictor and NFC as moderator. 
To evaluate the moderating effect, we will calculate the Johnson-Neyman interval.
<!--CS: Man könnte noch die Effektgröße bestimmen nach: doi: 10.1002/sim.3429 -> semi partial R²  -->

To ensure the validity of the MLM, we will conduct a specification curve analysis [@Simonsohn2020], which will include 63 possible preprocessing pipelines of the RT data.
These pipelines specify which transformation was applied (none, log, inverse, or square-root), which outliers were excluded (none, 2, 2.5, or 3\ $MAD$ from the median, RTs below 100\ or\ 200\ ms), and across which dimensions the transformations and exclusions were applied (across/within subjects and across/within n-back levels).
The MLM will be run with each of the 63\ pipelines, which will also include our main pipeline (untransformed data, exclusion of RTs below 100\ ms).
The ratio of pipelines that lead to significant versus non-significant effects will provide an indication of how robust the effect actually is.

@@

The results of each analysis will be assessed on the basis of both $p$-value and the Bayes factor $BF10$, calculated with the *BayesFactor* package [@Morey2021] using the default prior widths of the functions *anovaBF*, *lmBF* and *regressionBF* corresponding. <!-- hoffe, das reicht denen, denn wenn man genauer werden will, müsste man noch zwischen fixed und random effects priors unterscheiden, die zu allem Überdruß auch noch unterschiedliche Zahlenwerte haben, 1/2 für fixed und 1 für random bei anovaBF und lmBF, aber sqrt(2)/4 bei regressionBF -->

>>>>

To determine the influence of task performance on the association of SVs and *n*-back level, we will set up an MLM using the $lmerTest$ package [@Kuznetsova2017]. 
We will apply restricted maximum likelihood (REML) to fit the model.
First, we will calculate the intraclass correlation (ICC) on the basis of the null model. <!--CS: Wieso wird der ICC nur für das Null Modell berechnet ? Man könnte den doch auch für das full-model ebenfalls angeben und sehen, wieviel Varianzaufklärung hinzugekommen ist? -->
Second, we will estimate a random slopes model of SVs including *n*-back load level as level-1-predictor and, additionally, NFC as level-2-predictor. 
Within the model, we will control for *d'*, RT, correct, and post-correct trials.
$$
SV \sim level\ * NFC + d' + RT + correct + postcorrect + (level|subject)
$$
Level-1-predictors will be centered within cluster, whereas the level-2-predictor will be centered at the grand mean as recommended by Enders & Tofighi [-@Enders2007]. 
We will visually inspect the residuals of the final model.
The approximately normal distribution indicates no evidence to perform model criticism.  
Third, we will perform a simple slopes analysis with n-back level as predictor and NFC as moderator. 
To evaluate the moderating effect, we will calculate the Johnson-Neyman interval.
<!--CS: Man könnte noch die Effektgröße bestimmen nach: doi: 10.1002/sim.3429 -> semi partial R²  -->

To ensure the validity of the MLM, we will conduct a specification curve analysis [@Simonsohn2020], which will include 63 possible preprocessing pipelines of the RT data.
These pipelines specify which transformation was applied (none, log, inverse, or square-root), which outliers were excluded (none, 2, 2.5, or 3\ $MAD$ from the median, RTs below 100\ or\ 200\ ms), and across which dimensions the transformations and exclusions were applied (across/within subjects and across/within *n*-back levels).
The MLM will be run with each of the 63\ pipelines, which will also include our main pipeline (untransformed data, exclusion of RTs below 100\ ms).
The ratio of pipelines that lead to significant versus non-significant effects will provide an indication of how robust the effect actually is.

@@

The results of each analysis will be assessed on the basis of both $p$-value and the Bayes factor $BF10$, calculated with the *BayesFactor* package [@Morey2021] using the default prior widths of the functions *anovaBF*, *lmBF* and *regressionBF*. <!-- hoffe, das reicht denen, denn wenn man genauer werden will, müsste man noch zwischen fixed und random effects priors unterscheiden, die zu allem Überdruß auch noch unterschiedliche Zahlenwerte haben, 1/2 für fixed und 1 für random bei anovaBF und lmBF, aber sqrt(2)/4 bei regressionBF -->
